%----------------------------------------------------------------------------%

\documentclass[overlapped,line,letterpaper]{res}

\usepackage{ifpdf}

\ifpdf
  \usepackage[pdftex]{hyperref}
\else
  \usepackage[hypertex]{hyperref}
\fi

\hypersetup{
  letterpaper,
  colorlinks,
  urlcolor=black,
  pdfpagemode=none,
  pdftitle={Curriculum Vitae},
  pdfauthor={Allahbaksh Mohammedali Asadullah},
  pdfcreator={$ $Id: allahbaksh.tex,v 1.28 2008/03/15 22:53:52 jrblevin Exp $ $},
  pdfsubject={Curriculum Vitae},
  pdfkeywords={Software Engineering, Search Engine, Modularity, Concept Extraction, SETLabs, Infosys Technologies}
}

%%===========================================================================%%

\begin{document}

\begin{ncolumn}{2}
  Allahbaksh Mohammedali Asadullah		& Phone: (+91)
  09845505322 \\
  MS. Scholar, IIIT Bangalore    & {\tt Email:
  allahbaksh.ma@iiitb.ac.in} \\ 			
  Electronics City, Bangalore 560100, India. 
\end{ncolumn}





%---------------------------------------------------------------------------
% Document Specific Customizations

% Make lists without bullets and with no indentation
\setlength{\leftmargini}{0em}
\renewcommand{\labelitemi}{}

% Use large bold font for printed name at top of pages
\renewcommand{\namefont}{\large\textbf}

%---------------------------------------------------------------------------
\begin{resume}

%\name{Resume: Allahbaksh Mohammedali Asadullah}

\begin{center} \it \LARGE \b{Detailed Resume: Allahbaksh Mohammedali Asadullah} \end{center}
             		
%---------------------------------------------------------------------------
\section{\bf Education} 
{\it Research Scholar at International Institute of Information Technology} \hspace{10mm} July 2010 - Till date\\
  \\
{\it Bachelor of Engineering } 	\hspace{52mm} BVB College of Engg. \& Tech, Hubli. \\
Electrical \& Electronics Engineering \hspace{78.6mm}2001-2005.   
%---------------------------------------------------------------------------

\section{\bf Experience}

\begin{format}
\title{l}\dates{r}\\
\employer{l}\location{r}\\
\end{format}



\title{Product Technology Lead}
\employer{Infosys Labs, Infosys Ltd.}
\location{Bangalore}
\dates{Oct. 2010-Present}
\begin{position}
%Working as Product Technology Lead in Infosys Labs. on different products which are being taken into the market.
\end{position}


\title{Technology Lead}
\employer{SETLabs, Infosys Technologies Ltd.}
\location{Bangalore}
\dates{April. 2010- Sept. 2010}
\begin{position}
%Worked as Technology Lead in Infosys Labs. 
\end{position}


\title{Technology Analyst}
\employer{SETLabs, Infosys Technologies Ltd.}
\location{Bangalore}
\dates{Oct. 2009- March. 2010}
\begin{position}
%Worked as Technology Analyst in Infosys Labs. 
\end{position}


\title{Technology Specialist}
\employer{SETLabs, Infosys Technologies Ltd.}
\location{Bangalore}
\dates{March 2008 - Sept. 2009}
\begin{position}
%Worked as Technology Analyst in Infosys Labs. 
\end{position}

\title{Software Engineer}
\employer{SETLabs, Infosys Technologies Ltd.}
\location{Bangalore}
\dates{Dec. 2005- Feb. 2008}
\begin{position}
%%Working as a Software Engineer in Software Engineering Center of Excellence: the core
%area code modularization and analysis. 
 
\end{position}

%---------------------------------------------------------------------------%


%------------------------------------------------------------------------------


\section {\bf Research Interests}
Software Engineering, Web 2.0, Cloud Computing, User Interface Design, Semantic Web, Algorithms \& Web Search.

\section{\bf Speaker}
%\begin{itemize}
\begin{enumerate}
\item Speaker at Google Technology User Group (GTUG, Dubai) on Google Web Technology July 2011.
\item Speaker at 2nd Indic Thread Cloud Computing conference on Map Reduce 3-4 June 2011.
\item Speaker at Great Indian Developer Summit on HTML5 with GWT and Architecturing for performance with GWT 20-21 April 2011.
\item Speaker at ACM Compute on HTML5 organized by ACM Bangalore on 25-26 March 2011.
\item Speaker at RIA workshop organized by ACM Bangalore on Google Web Toolkit 2.1 features on 12 June 2010.
\item Speaker at Indic Thread Java Conference on GWT Internals, Tips and Tricks 9-10 Dec 2009.
\item Speaker at Indic Thread Java Conference on Lucene (A Full Text Search Library) 9-10 Dec 2009.
\item Speaker at Dev Camp  2009 organized by Thought Works Bangalore on GWT Defered Binding and GWT compiler
\item Speaker at BarCamp Bangalore 2008 on Google Web Toolkit.

\end{enumerate}
%\end{itemize}
%------------------------------------------------------------------------------

\section{\bf Teaching Experience}
\begin{itemize}
\item Taught a course on Cloud computing at IIIT Jabalpur, MP, India
\item Teaching Assistant on Hadoop at IIIT Bangalore
\item (EDA Tool) \& WinSpice tutor for two days for staff and
student of Electronics \& Communication Dept. B. V. Bhoomaraddi College of Engg.
\& Tech.
\item Teaching Assistant for VLSI course organized by VAT Cell, B. V. Bhoomaraddi
College of Engg. \& Tech., Hubli.
\item Teaching Assistant for MATLAB course for students of VI semester.
\end{itemize}

%------------------------------------------------------------------------------



\section{\bf Consulting Projects}
\textit{\textbf Toyota Motor Europe} - May-July 2010
\\
Toyota Motors Europe Application Support Workbench - I was involved in designing and developing a reference implementation of the Work bench using GWT 2.0 and also adhering to best design practices like Model View Presenter etc. I lead a team of 10  developers to achieve the solution.

\textit{\textbf Nike USA} - Jan-Feb 2011
\\
Was instrumental in technological decisions and architecture definition of Nike project using GWT, GIN, Guice etc. 

%\textit{\textbf }


\section{\bf Patents Applied }
\begin{itemize}
\item Patent Applied for: \textit{"Online Structural Search of Source Code for Large Software Systems"}, Allahbaksh Asadullah, Basavaraju Muddu, Krishnakumar Pooloth. 
\item Patent Applied for: \textit{"A System and Method for Effective Search and classification of Source Code Online."}, Allahbaksh Asadullah, Basavaraju Muddu, Susan George.
\item Patent Applied for: \textit{"Code Edit - An Online Java Source Code Editor with Code Assist"}, Allahbaksh Asadullah, Basavaraju Muddu, Susan George. 
\item Patent Applied for: \textit{"System and Method for Reducing Storage in Cloud Softwares"}, Allahbaksh Asadullah, Basavaraju Mudu, Srinivas P.
\item Patent Applied for: \textit{"System and Method for Plagiarism detection in Object Oriented Systems using Reduction of Abstraction"},Allahbaksh Asadullah, Basavaraju Mudu, Srinivas P., Vasudev Bhat.
\item Patent Applied for: \textit{"System and Method for Plagiarism detection in Pattern based Software Systems"},Allahbaksh Asadullah, Basavaraju Mudu, Srinivas P., Ilan.
\end{itemize}

\section{\bf Distinct Contribution}
One among the finalists for WWW 2011 workshop. Our entry CodeEdit is an online platform for Java Editor with Code Completion feature. It is fully implemented using GWT. I am responsible for Architecting the same.\\
Team Members: Allahbaksh Asadullah, Basavaraju M., Susan George



%------------------------------------------------------------------------------


\section{\bf Awards \& Distinction}
\begin{itemize}
\item Best InStep Project Mentor award in Technical Stream for first half of 2011.
\item Best Innovator Award, SETLabs Infosys,for Quarter 1, 2010 - 2011.
\item  Best Outgoing Student of Department of Electrical and Electronics for
the year 2004-2005. \\
\item  Won 3rd Prize (Bronze Medal) at IEEE Techscribe a National Level Paper.
Presentation Competition at IIT-Guwahati on 4th 5th September 2004. \\
\item  Won the 1st prize at State level Student Paper Contest MANTHAN-2004 organized  by IEEE Student Chapter \& SAE – India BVB Collegiate Club,
BVBCET, Hubli on 14th May 2004 for Paper titled \textit{"Cost Oriented Design of DAC for SOC Environment"}.\\	
\item  Won the 1st prize at 2nd State level Student ISTE Student Convention
organized for Paper titled \textit{"Design \& Simulation of On Chip Reconfigurable  Logic Circuits Using Error Back Propagation Algorithm"}.\\
\item  Won 1st prize at National Level Student Paper Contest {"KSHITIJ 04"}
organized by IEEE Student Chapter BEC, Bagalkot on 15-17 October 2004 for Paper titled \textit{"Design of 3.3v 
 Current Mode DAC Macrocell"}. 
\end{itemize}

%------------------------------------------------------------------------------

\section {Reports and Thesis}
\begin{itemize}
\item Allahbaksh Mohammedali Asadulllah, \textit{"Reducing the time complexity of Bin Packing problem"}, MS Thesis [Work In Progress]. 
\item Allahbaksh Mohammedali Asadulllah, \textit{"Design \& Simulation of
Inverse Time Characteristics  Circuit"}, BE Thesis. 
\item Allahbaksh Mohammedali Asadulllah, \textit{"Design \& Simulation of 8-Bit
Current Steering DAC."}, Prefinal Thesis.
\end{itemize}



\section{\bf Leadership Skills}
\begin{itemize}
\item Best InStep Project Mentor Award Infosys Ltd 2011.
\item Mentored interns from different geographic locations.
\item Organized BarCamp Hubli on July 12 2008
\item I led the team of four to send Buisness Idea to Centre for Innovation
Incubation and Entrepreneurship (CIIE , IIM - Ahmedabad)in which we reached
interview stage.
\item Student Vice Chair of BVB IEEE Student Chapter 2004-2005.
\item Secretary of Electrical \& Electronics Student Association (EESA) at BVB
College of Engg, Hubli. %\& Tech.
\item Organized two state level workshops as Student Secretary  of Department.
\item Organized several College Level workshops as Student Secretary  \& IEEE
Vice Chair.
\item Attended Leader Workshop at IIT-Guwahati.
\item Represented department during NBA, ISO \& AICTE visits.   
\end{itemize}


%%===========================================================================%%


%\section{\bf Systems Developed} 

%\begin{tabular}{|l|l|l|}
%\hline
%$System Developed$ 		    	&	$Duration$ 	   	&   $Role$ \\
%\hline
%
%\small SLIM - Intelligent Modularization of &  May 2007 - Current	& \small
%Software Engineer \\
%\smalland Large System.  &	   	& \small Infosys Research  \\
%\hline
%\small ICode - A Java Source Code Search,	&  Jun 2006 - April 2007	& \small
%Software Engineer \\
%\smalland Browse \& Impact Analysis Engine.  &	   	& \small Infosys Research  \\
%\hline
%\end{tabular}

%------------------------------------------------------------------------------


%%===========================================================================%%


\section{\bf Current Research Work (at Infosys Labs) [Dec 2005 - Present] }
\texit{\textbf iPlag - Source Code Plagiarism Detection}\\
In this project we explore different method of plagiarism detection in source code. We are working on some of the algorithms which can scale well and also identify the plagiarism given a source code.
\textit{Status:} In progress.
\textit{\textbf MSR - Mining Software Repositories} \\
MSR is a new upcoming area of research. It involves usage of historic information available in version and bug repositories 
for bug prediction so that the project managers can plan their resource allocation based on bugginess of the programs and manage
the software releases accordingly. \\
\textit{Status:} In progress.

\textit{\textbf ICode - Java Code Search and Analysis Engine} \\
ICode is a vertical search engine for source code. It retrieves source code fragments/elements based on the search string. It supports specialized queries suitable for searching source code. 
%A general purpose search engine would support query constructs that allows for more targeted search.  
For e.g., Google supports constructs to search from specific domains, search for text in title or url of a web page etc. Similarly, ICode allows a user to search for words in method name, comment, class name etc. 
%ICode also provides subset features of an IDE on browser. This helps developer in several ways. 
Few of features include syntax highlighting, Code Browsing, IDE like interface, Quick search from code etc.\\
\textit{Status:} Completed and now used across business units in Infosys.  

\textit{\textbf SLIM - Intelligent Modularization of Large System} \\
This project measures quality of code. We have built a set of tools which helps to analyze the source code. We are extracting facts from the source code by customizing some of open source parsers. The facts extracted are analyzed and used for computation of modularity metrics of the same, and also the facts are now subjected to concept analysis.\\
\textit{Status:} Completed.
 
%------------------------------------------------------------------------------


%------------------------------------------------------------------------------

%\section{\bf Other academic projects}
%\begin{itemize}
%\item Design \& Simulation of {"On Chip Reconfigurable  Logic Circuits Using
%Error Back Propagation   Algorithm"}.
%\item Design and Development of 8085 processor based Current and Voltage relay.
%\item Design and Implementation of IEEE floating point algorithm for fixed point
%(8085) processor.   
%\item 
%\end{itemize}

%------------------------------------------------------------------------------

\section{\bf Skillset}
\begin{ncolumn}{2}
  Operating Systems   		& GNU/Linux, Windows 98/2000/XP/7 \\
  Java Technologies			& Java, Servlet, JSP, Eclipse Plugins, Lucene, Solr, AppEngine, Hadoop, Guice, Apache JDO \\
  DBMS						& MySql, CouchDB, Apache Derby	\\
  Web Technologies			& GWT, HTML, HTML5, CSS, JavaScript \\
  Version Control System	& SVN, CVS, GIT, Mercurial\\
  EDA Tools					& LASI, Tanner SEdit, Spice \\
\end{ncolumn}


%------------------------------------------------------------------------------

\section{\bf References}

\begin{ncolumn}{2}
  Prof. Dinesha,        	& Dr. Srinivas Padmanabhuni,\\
  Software Engineering Lab, & Principal Research Scientist \& Associate VP,\\
  International Institute of Technology, 		& Infosys Labs, Infosys Ltd.,\\
  Hosur Road, Bangalore 560100 				& Hosur Road, Bangalore 560100.\\
  Email: dinesha@iiitb.ac.in			 	 			& Email: srinivas\_p@infosys.com\\
\end{ncolumn}

\pagestyle {plain}


\end{resume}
\end{document}

%%===========================================================================%%, 26/C, Electronics 